---
output: rmarkdown::github_document
editor_options: 
  chunk_output_type: console
---
```{r pkg-knitr-opts, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE, fig.retina = 2, message = FALSE, warning = FALSE
)
options(width=120)
```

[![Travis-CI Build Status](https://travis-ci.org/hrbrmstr/ggeconodist.svg?branch=master)](https://travis-ci.org/hrbrmstr/ggeconodist) 
[![Coverage Status](https://codecov.io/gh/hrbrmstr/ggeconodist/branch/master/graph/badge.svg)](https://codecov.io/gh/hrbrmstr/ggeconodist)
[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/ggeconodist)](https://cran.r-project.org/package=ggeconodist)

# ggeconodist

Create Diminutive Distribution Charts

## Description

'The Economist' has a unique boxplot aesthetic f or
communicating distrribution characteristics. Tools are provided
to create similar charts in 'ggplot2'.

Inspired by: <https://www.economist.com/united-states/2019/06/29/will-transparent-pricing-make-americas-health-care-cheaper>

## What's Inside The Tin

```{r ingredients, results='asis', echo=FALSE, cache=FALSE}
hrbrpkghelpr::describe_ingredients()
```

The following functions are implemented:

## Installation

```{r install-ex, results='asis', echo = FALSE}
hrbrpkghelpr::install_block()
```

## Usage

```{r lib-ex}
library(ggeconodist)

# current version
packageVersion("ggeconodist")

```

### The whole shebang

**YOU WILL NEED** to install [these fonts](https://github.com/economist-components/component-typography) to use the built-in theme. More on how to do that at some point.

```{r}
ggplot(mammogram_costs, aes(x = city)) +
  geom_econodist(
    aes(ymin = tenth, median = median, ymax = ninetieth),
    stat = "identity", show.legend = TRUE
  ) +
  scale_y_continuous(expand = c(0,0), position = "right", limits = range(0, 800)) +
  coord_flip() +
  labs(
    x = NULL, y = NULL,
    title = "Mammoscams",
    subtitle = "United States, prices for a mammogram*\nBy metro area, 2016, $",
    caption = "*For three large insurance companies\nSource: Health Care Cost Institute"
  ) +
  theme_econodist() -> gg

grid.newpage()
left_align(gg, c("subtitle", "title", "caption")) %>% 
  add_econodist_legend(econodist_legend_grob(), below = "subtitle") %>% 
  grid.draw()
```

## ggeconodist Metrics

```{r cloc, echo=FALSE}
cloc::cloc_pkg_md()
```

## Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). 
By participating in this project you agree to abide by its terms.
