---
output: rmarkdown::github_document
editor_options: 
  chunk_output_type: console
---
```{r pkg-knitr-opts, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE, fig.retina = 2, message = FALSE, warning = FALSE
)
options(width=120)
```

[![Travis-CI Build Status](https://travis-ci.org/hrbrmstr/ggeconodist.svg?branch=master)](https://travis-ci.org/hrbrmstr/ggeconodist) 
[![Coverage Status](https://codecov.io/gh/hrbrmstr/ggeconodist/branch/master/graph/badge.svg)](https://codecov.io/gh/hrbrmstr/ggeconodist)
[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/ggeconodist)](https://cran.r-project.org/package=ggeconodist)

# ggeconodist

Create Diminutive Distribution Charts

## Description

'The Economist' has a unique boxplot aesthetic f or
communicating distrribution characteristics. Tools are provided
to create similar charts in 'ggplot2'.

Inspired by: <https://www.economist.com/united-states/2019/06/29/will-transparent-pricing-make-americas-health-care-cheaper>

## What's Inside The Tin

```{r ingredients, results='asis', echo=FALSE, cache=FALSE}
hrbrpkghelpr::describe_ingredients()
```

The following functions are implemented:

## Installation

```{r install-ex, results='asis', echo = FALSE}
hrbrpkghelpr::install_block()
```

## Usage

```{r lib-ex}
library(ggeconodist)

# current version
packageVersion("ggeconodist")

```

### The whole shebang

**YOU WILL NEED** to install [these fonts](https://github.com/economist-components/component-typography) to use the built-in theme. More on how to do that at some point.

```{r}
ggplot(mammogram_costs, aes(x = city)) +
  geom_econodist(
    aes(ymin = tenth, median = median, ymax = ninetieth),
    stat = "identity", show.legend = TRUE
  ) +
  scale_y_continuous(expand = c(0,0), position = "right", limits = range(0, 800)) +
  coord_flip() +
  labs(
    x = NULL, y = NULL,
    title = "Mammoscams",
    subtitle = "United States, prices for a mammogram*\nBy metro area, 2016, $",
    caption = "*For three large insurance companies\nSource: Health Care Cost Institute"
  ) +
  theme_econodist() -> gg

grid.newpage()
left_align(gg, c("subtitle", "title", "caption")) %>% 
  add_econodist_legend(econodist_legend_grob(), below = "subtitle") %>% 
  grid.draw()
```

```{r}
library(dplyr)
library(patchwork)
library(hrbrthemes)
library(gapminder)

p <- ggplot(mpg, aes(class, hwy)) + theme_ipsum_rc()

(p + geom_boxplot()) +
(p + geom_econodist(width = 0.25)) +
  plot_layout(ncol = 1)

(p + geom_boxplot() + coord_flip()) +
(p + geom_econodist(tenth_col = ft_cols$blue, ninetieth_col = ft_cols$red) +
   coord_flip()) +
  plot_layout(ncol = 1)

(p + geom_boxplot(aes(fill = factor(drv)))) +
  (p + geom_econodist(aes(fill = factor(drv)))) +
  plot_layout(ncol = 1)
```

```{r gm, fig.width=600/72, fig.height=700/72}
gapminder %>%
  filter(year %in% c(1952, 1962, 1972, 1982, 1992, 2002)) %>%
  filter(continent != "Oceania") %>%
  ggplot(aes(x = factor(year), y = lifeExp, fill = continent)) +
  geom_econodist(
    median_point_size = 1.2,
    tenth_col = "#b07aa1",
    ninetieth_col = "#591a4f",
    show.legend = FALSE
  ) +
  ggthemes::scale_fill_tableau(name = NULL) +
  coord_flip() +
  labs(
    x = "Year", title = "Life Expectancy", y = NULL,
    caption = "Example borrowed from @cmdline_tips"
  ) +
  facet_wrap(~continent, nrow = 4) +
  theme_ipsum_rc() -> gmgg

grid.newpage()
gmgg %>% 
  add_econodist_legend(
    econodist_legend_grob(
      tenth_col = "#b07aa1",
      ninetieth_col = "#591a4f",
    ), 
    below = "axis-b-1-4", 
    just = "right"
  ) %>% 
  grid.draw()
```

## ggeconodist Metrics

```{r cloc, echo=FALSE}
cloc::cloc_pkg_md()
```

## Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). 
By participating in this project you agree to abide by its terms.
